---
title: "Creating Markdown Presentation and Plotly Graphs"
author: "Renata Guanaes"
date: "02/04/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Description

This is a task from **Peer-graded Assignment: R Markdown Presentation & Plotly**, Develop Data Product Course, Week 03.

Create a web page presentation using R Markdown that features a plot created with Plotly. <br><br>
Host your webpage on either GitHub Pages, RPubs, or NeoCities. <br><br>
Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

## About dataset

- Dataset: Housing Values in Suburbs of Boston
- Verify relationship between lower status of the population (lstat) x median value of the house
- Verify relationship between per capita crime rate (crim) x median value of the house


```{r message=FALSE, warning=FALSE, include=TRUE}
suppressMessages(library(MASS))
suppressMessages(library(plotly))
data(Boston)
attach(Boston) 
```


## Dataset summary

```{r echo = TRUE}
summary(Boston[c('lstat','crim', 'medv')])
```

## Plot: Boston Houses - Price (medv) x lower status (Lstat)
```{r }
p1 = plot_ly(Boston, x=lstat, y=medv, 
              type="scatter", 
              mode="markers",
              marker = list(size=10, opacity=.9),
              color = medv,
              colors = 'plasma'
             )
colorbar(p1)

```


## Plot: Boston Houses - Price (medv) x Crime Rate
```{r }
p = plot_ly(Boston, x=crim, y=medv, 
            type="scatter",
            mode="markers",
            marker = list(size=10, opacity=.9),
            color = medv, 
            colors = 'viridis'
        )

colorbar(p)
```

