---
title: "Brazil_InteractiveMap"
author: "Renata Guanaes"
date: "02/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Course Project"
author: "Renata Guanaes Machado"
date: "02/04/2021"
output:
  html_document: default
  pdf_document: default
subtitle: Develop Data Products (*from Data Science Specialization*)
---


## **Executive Summary**
This is a task from **Peer-graded Assignment: R Markdown and Leaflet**, Develop Data Product Course, Week 02.

Create a web page using R Markdown that features a map created with Leaflet. <br>
Host your webpage on either GitHub Pages, RPubs, or NeoCities. <br>
Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 


### **Libraries**

```{r message=FALSE, warning=FALSE, include=TRUE}

suppressMessages(library(leaflet))
suppressMessages(library(htmltools))
suppressMessages(library(readr))
```

### **Loading Data**
Brazil Cities Database: List of **50 prominent cities in Brazil**. <br> Each row includes a city's latitude, longitude, state and population, among other variables.

Data from: https://simplemaps.com/data/br-cities

```{r}
setwd("~/data")
data <- read.csv(file = "Brazil_475ProminentCities.csv", 
                    header = TRUE, 
                    encoding = "UTF-8",
                    sep = ",")

data <- data[, c(1,2,3,6,8)] # maintain the relevant columns
colnames(data) <- c('City','Latitude','Longitude','State', 'Population')

# filtering only the 100 most prominent cities
data100 <- head(data[order(data$Population, decreasing=TRUE),], 100)

head(data100, 5)
```




```{r}
data100 %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions()) %>%
  addMarkers(popup=paste
              ("<br>State: ", htmlEscape(data100$State),
               "<br>City: ",  htmlEscape(data100$City),
               "<br>Population: ",  htmlEscape(data100$Population/1000)
                          ))



```


